Manuscript Figures for Genome Biology

### 2018-07-23 manuscript_figures/manuscript_figures.Rmd
Adjust y-axis of figure 6c after filtering GSEA tests

pc <- strat_hist(res, pvalue = "pval",
           covariate = "ind_covariate", maxy = 35, axislabs = FALSE) +
  draw_plot_label("  GSEA case study: Mouse", 0.5, 1, hjust = 0.5, fontface = "bold" , size = 12) +
  draw_plot_label("Gene Set size pvalue", size = 11, 0.5, 0.14, fontface = "plain",
                  hjust =0.5) +
  draw_plot_label("Density", size = 11, 0, 0.36, fontface = "plain", angle=90)

>>>>

pc <- strat_hist(res, pvalue = "pval",
           covariate = "ind_covariate", maxy = 7, axislabs = FALSE) +
  draw_plot_label("  GSEA case study: Mouse", 0.5, 1, hjust = 0.5, fontface = "bold" , size = 12) +
  draw_plot_label("Gene Set size pvalue", size = 11, 0.5, 0.14, fontface = "plain",
                  hjust =0.5) +
  draw_plot_label("Density", size = 11, 0, 0.36, fontface = "plain", angle=90)
